---
title: |
 | Analysis Report
 | List of asthma medications in primary care prescriptions and in self-reported medications
 | -
 | Differentiate in 'all asthma', 'mild', 'mild-moderate' and 'severe' disease
author: "Noemi-Nicole Piga"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: "hide"
    toc: true
    toc_float: true
    theme: united
---

```{r, setup, hide = TRUE}
library(reticulate)

# To run this .rmd file:
#be in the folder with the .Rmd file
#export PATH=${PATH}:/cm/shared/apps/R/deps/rstudio/bin/pandoc
#file="./Asthma_meds_severity.Rmd"
#module load R
#Rscript -e 'rmarkdown::render("'$file'")'
```

# Rationale
Use the list of asthma medication from primary care prescription found by Mike to divided participants with diagnosed asthma
and a primary care prescription for asthma into 'all asthma', 'mild', 'mild-moderate' and 'severe' disease.
Compare this list with the list of medication from self-reported medications (data field 20003) used in the Lancet Paper
and try to divide this medication into the four disease group as well.

# Analysis
Code: Asthma_meds_severity.sh; Asthma_meds_severity.R
```{bash, code = readLines('/home/n/nnp5/PhD/PhD_project/UKBiobank_datafields/scripts/Asthma_meds_severity.sh'), eval=FALSE}
```
```{r, code = readLines('/home/n/nnp5/PhD/PhD_project/UKBiobank_datafields/scripts/Asthma_meds_severity.R'), eval=FALSE}
```